### 2021-04-21 evaluation.tex
Specify figure placement with [ht] > [h]
Justification: https://tex.stackexchange.com/a/1527/202639
Correct an invalid reference: Vampire
Remove a todo we have decided to pass

The empirical evaluation was performed using a modified version of the \gls{atp} \Vampire{} 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
\todo[author=R2]{the reference for Vampire ([20]) describes version 2.6 of Vampire and you are using version 4.3. If available, something more recent would give a better idea of the current capacities of Vampire.}
The prover was used to generate the training data and to evaluate the trained precedence recommender.
To generate the training data,
\Vampire{} was modified to output \gls{cnf} representations of the problems
and annotated problem signatures in a machine-readable format.
%in \gls{json} format and annotated problem signatures in \gls{csv} format.\todo{MS: Mentioning JSON or CSV seems to be too low level. ``programmer documatation'' material.}
For the evaluation of the precedences generated by the recommender,
\Vampire{} was modified to allow the user to supply explicit predicate and function symbol precedences for the proof search
(normally, the user only picks a precedence generation heuristic).
The modified version of \Vampire{} is available online.\footnote{\url{https://github.com/filipbartek/vampire/tree/cade28}}
% https://github.com/filipbartek/vampire/tree/3bbfa9e6cd009f501f74d26eabc7e7811b5bb00e
\todo{MS: nebo jeste lip. Slo by udelat repo,
ve kterym bude textak, co vsechno vysvetli, vcetne linku na ty dve repa co zminujes tady a vyse.}

@@

\begin{table*}[h]
\caption{
Results of the evaluation of symbol precedence heuristics based on various symbol cost models
on $\ProblemsVal$ ($\card{\ProblemsVal} = 7648$).
Means and standard deviations over 5 runs are reported.
The \gls{gcn} models were trained according to the description in \cref{sec:architecture,sec:training,sec:evaluation}.
The model Simple is the final linear model from our previous work \cite{DBLP:conf/cade/Bartek020}.
The models that used \acrlong{ml} only for the predicate precedence
used the \texttt{frequency} heuristic for the function precedence, and vice versa.
The frequency model uses the standard \texttt{frequency} heuristic for both predicate and function precedence.
}
\label{tab:results}
\centering
\begin{tabular}{l|ll|rl}

@@

\todo[inline,author=R1]{Despite the clear improvement over baseline, the percentage gained does not appear
to be too big. It is possible, that the potential effect of better orderings is not
too high, regardless of the optimizations. Can you give some insights for this
line of thought?
}

>>>>

The empirical evaluation was performed using a modified version of the \gls{atp} \Vampire{} 4.3.0 \cite{DBLP:conf/cav/KovacsV13}.
\todo[author=R2]{the reference for Vampire ([20]) describes version 2.6 of Vampire and you are using version 4.3. If available, something more recent would give a better idea of the current capacities of Vampire.}
The prover was used to generate the training data and to evaluate the trained precedence recommender.
To generate the training data,
\Vampire{} was modified to output \gls{cnf} representations of the problems
and annotated problem signatures in a machine-readable format.
%in \gls{json} format and annotated problem signatures in \gls{csv} format.\todo{MS: Mentioning JSON or CSV seems to be too low level. ``programmer documatation'' material.}
For the evaluation of the precedences generated by the recommender,
\Vampire{} was modified to allow the user to supply explicit predicate and function symbol precedences for the proof search
(normally, the user only picks a precedence generation heuristic).
The modified version of \Vampire{} is available online.\footnote{\url{https://github.com/filipbartek/vampire/tree/cade28}}
% https://github.com/filipbartek/vampire/tree/3bbfa9e6cd009f501f74d26eabc7e7811b5bb00e
\todo{MS: nebo jeste lip. Slo by udelat repo,
ve kterym bude textak, co vsechno vysvetli, vcetne linku na ty dve repa co zminujes tady a vyse.}

@@

\begin{table*}[ht]
\caption{
Results of the evaluation of symbol precedence heuristics based on various symbol cost models
on $\ProblemsVal$ ($\card{\ProblemsVal} = 7648$).
Means and standard deviations over 5 runs are reported.
The \gls{gcn} models were trained according to the description in \cref{sec:architecture,sec:training,sec:evaluation}.
The model Simple is the final linear model from our previous work \cite{DBLP:conf/cade/Bartek020}.
The models that used \acrlong{ml} only for the predicate precedence
used the \texttt{frequency} heuristic for the function precedence, and vice versa.
The frequency model uses the standard \texttt{frequency} heuristic for both predicate and function precedence.
}
\label{tab:results}
\centering
\begin{tabular}{l|ll|rl}

@@
